X-ray phase-contrast imaging at \SI{100}{\kilo\electronvolt} on conventional sources

### 2013-10-24 point_by_point_response.tex

%        File: point_by_point_response.tex
%     Created: Wed Oct 23 05:00 PM 2013 C
% Last Change: Wed Oct 23 05:00 PM 2013 C
%
\documentclass[a4paper,english]{scrartcl}
\usepackage[detect-all]{siunitx}
\usepackage{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc} %Umlaute

\DeclareSIUnit{\voltpeak}{Vp}

@@

\title{Point-by-point response to the reviewers}
\date{}
\begin{document}
\maketitle

\section*{Reviewer \#1}
\begin{quote}
    I could not find a significant advance in this work. X-ray Talbot-Lau
    interferometers with high-energy x-rays have been already reported (Ref.
    18-20, 23, D. Stutman et al., Appl. Opt. 49 (2010) 4677 etc.). The
    authors mention that the edge-on- illuminated grating interferometry
    breaks the current limitations of x-ray phase-contrast imaging, but I
    don't think that there is clear evidence showing that the authors'
    method is much more promising than the methods reported in the previous
    papers. If the authors want to show that the edge-on-illumination method
    is by far the most promising for high-energy and large-field-of-view
    x-ray phase imaging, I think that the authors have to quantitatively
    compare the method with those previously reported in terms of the total
    exposure time, spatial resolution, signal-to-noise ratio, and so on, and
    show that the authors' method is much better than the others.
\end{quote}
We think that the experiments presented in the current manuscript show
indeed significant progress with respect to the cited references.
The method presented by Stutman et al. has a fundamental limitation that
prevents it from achieving curved structures and large aspect ratios.
Moreover, those experiments were performed on a source
with~\SI{60}{\kilo\voltpeak}, which is significantly lower than
the~\SI{160}{\kilo\voltpeak} of our source and the~\SI{100}{\kilo\eV} used
as the design energy for our interferometer.

The other works also present results in a much lower energy range or very
different conditions, thus preventing a meaningful comparison.
Reference~23 reported images taken at \num{30} and~\SI{60}{\kilo\eV},
reference~20 also has a design energy of~\SI{47.9}{\kilo\eV}. Finally,
references~18 and~19 present Talbot interferometry at~\num{82}
and~\SI{123}{\kilo\eV} respectively, but only the first result is published
on a peer reviewed journal, and both experiments were performed at the ESRF
synchrotron, with a monochromatic and coherent beam that is incomparable to
a conventional tube.

\begin{quote}
    Furthermore, the authors mention that the results in Fig. 3 show the benefit of the phase nature of the image, but I think that the authors should provide a more detailed explanation about the contrasts in the images because the contrast of soldering points underneath the resistors should not be reduced in the differential attenuation image for monochromatic x-rays. The authors should explain quantitatively why the contrast is reduced. Otherwise, the authors' assertion is suspicious.
\end{quote}
A paragraph was added to discuss the different beam hardening behaviour of
the absorption and differential phase image to address the reviewer's
concerns.

\section*{Reviewer \#2}
\begin{quote}
    However, this solution comes with significant drawbacks in terms of very
    limited fields of view~\SI{3}{\centi\metre} horizontally, a single detector pixel in the vertical direction), which at the moment seem hard to overcome.
\end{quote}
There is no fundamental limitation on the horizontal field of view in our
approach. On the contrary, our solution actually solves precisely this
issue, by easily matching the spherical wave front with the curved
structures. Any limitation to horizontal the field of view given by large glancing
angles is therefore removed. The gratings could already be fabricated on
larger wafers with the existing technology.

The limitations in the vertical field of view do not come at the expense of
an increased dose with our proposed scanning solution. Larger areas could in
principle be scanned with short exposure times by stacking an array of
edge-illuminated gratings. This scanning technique is already offered in commercial X-ray
diagnostic devices, such as the Philips MicroDose mammography system, to
reduce scattering.

\begin{quote}
    Moreover, in the methods section the authors talk of a
    \SI{5}{\percent} visibility, which is even lower than that of the quoted papers by Pfeiffer's group (refs 18, 19), which, at least nominally, reach even higher energies (123 keV). Hence, the reduction in field-of-view does not seem to be counterbalanced by significant improvements in visibility. This is also supported by the relatively poor quality of the differential phase image compared to the derivative of the absorption image, where the only advantage seems to be the visibility of the soldering points beneath the resistors (primarily due to the fact that these do not produce area contrast in the DPC image), while everywhere else the contrast of the differentiated absorption image seems to be higher.
\end{quote}
The visibility in our experiment is still low, and this obviously
affects the quality of the images, but we also mentioned
that this is the first attempt in building gratings with our new design,
while the fabrication of traditional structures has been developed for over
a decade now. The remarks above about references~18 and~19 (synchrotron
source, unpublished results) should also be taken into account here.
\begin{quote}
Finally, the novelty of the result is diminished by previous demonstrations that high energies in phase-contrast x-ray imaging could be reached by other methods (e.g. Ignatyev et al JAP 110 (2011) 014906), albeit in that case image quality seems to be lower.     
\end{quote}
In the paper from Ignatyev et al., an admittedly lower image quality was
achieved again with softer X-rays, from~\num{60}
to~\SI{100}{\kilo\voltpeak}. Thus, we claim that our results
are a significantly more promising than the technique described therein.

@@

\section*{Reviewer \#3}

\begin{quote}
    An extended object is imaged by axial scanning, which results in very
    long exposure times due to phase stepping.  The legend of Fig. 3
    indicates that one image line of \SI{0.1}{\milli\metre} width is
    acquired in \SI{6}{\minute}.  The authors admit this situation in the last sentences of the manuscripts without giving a convincing solution to the problem.
\end{quote}
This is indeed an issue, as the exposure time is mostly affected by the low visibility. The manuscript
was amended to include a more detailed discussion of our plans to reduce
the exposure time. We briefly mention here that raising the visibility to
\SI{15}{\percent}, a value already reached in lower energy experiments,
would immediately cut the exposure by \num{9} times.
\begin{quote}
    The authors suggest that the only imaging methods that can be used with
    conventional x-ray sources are the in-line phase contrast technique and
    Talbot interferometry. They fail to mention that analyzer-based imaging
    systems with x-ray tube sources have been built and successfully used
    for imaging rather large biological objects. The current exposure times
    are shorter or comparable to those of the present work, but there are
    clear indications how the exposure times in x-ray tube based ABI can be
    reduced by an order of magnitude or more. On the other hand, the upper
    limit of photon energy is that of the tungsten Kalpha line,
    \SI{60}{\kilo\eV}. For references, see Nesch et al.(2009), Rev. Sci.
    Instrum. 80, 093702, and Parham et al.(2009), Acad.Radiol. 16, 911-917.
\end{quote}
We now included references to these papers, but we point out that our
experiments do not have any intrinsical limit to the photon energy.
\end{document}

### 2013-10-24 appeal_letter.tex
latest appeal letter

We have recently received a negative decision on our
manuscript \textsc{NCOMMS-13-09247-T}. We would like to formally appeal this
decision and ask for the permission to submit a revised version of our
manuscript addressing the concerns of the reviewers. The reason for our
appeal is mainly driven by the motivations raised by the reviewers against
our work which we found not fully correct and, in some cases, even too
simplistic. For your convenience, we will briefly summarize our arguments in
the following lines.

Referee one would actually welcome a revised manuscript, addressing his/her
comments and is not advising a rejection a priori. The mentioned work of
Stutman et al has an intrinsic limitation (the tilt angle) which our
approach does not have. Exactly this issue prevents the methods of Stutman
to achieve sufficiently high-aspect ratio \emph{and} curved profiles at the same
time, something that our method easily can. The problem mentioned on the
contrast below the soldering points can be explained by beam-hardening in
the absorption image. We would amend the manuscript accordingly, providing
more information as requested.

Referee two is skeptical about the visibility achieved in our experiment
compared to the work from Pfeiffer's group. He/she might not have noticed
that our data have been obtained on a commercially available X-ray tube,
while the cited experiment of Pfeiffer's et al. has been carried out at a
    third generation synchrotron source, where notably unsurpassed beam
    conditions can be created which are far from what one can expect in real
    life (i.e. with conventional X-ray tubes). And, even if one would like
    to still carry out this (unfair) comparison, we should mention that our
    experiment is the \emph{first} measurement of its kind with the first
    generation of gratings made according to our innovative design.
    Pfeiffer's team uses gratings obtained after almost a decade of
    development and, despite this and the use of a synchrotron, they are not
    much further than us and still carry the intrinsic limitation of a
    limited grating height. We are perfectly aware that the quality of our
    images has still to be improved, but here we are presenting the first
    experiments with edge-on grating illumination, describing its great
    potential but also acknowledging its (temporary) limitations. The same
    reviewer also complain about the limited field-of-view and a potentially higher
    dose that our method would generate compared to previous solutions. Both
    arguments are wrong, since the horizontal field-of-view is just limited by the
    size of the wafer (as for other methods) while the vertical
    field-of-view is
    covered by a vertical scan of the sample, i.e. not limited at all, and,
    more important, it does not require a higher dose. Reviewer 2 finally
    admits that in comparison with a coded-aperture based experiment at 100
    kVp our images (taken at 160 kVp) are better, which we of course
    appreciate. We believe that novelty in the approach must be the driving
    factor in judging the suitability of our work for this journal and not
    the present limitations of the technology (which can be solved!), as
    reviewer 2 seems to conclude.

>>>>

We have recently received a negative decision on our manuscript NCOMMS-13-09247-T. We would like to formally appeal this decision and ask for the permission to submit a revised version of our manuscript addressing the concerns of the reviewers. The reason for our appeal is mainly driven by the motivations raised by the reviewers against our work which we found not fully correct and, in some cases, even too simplistic. For your convenience, we will briefly summarize our arguments in the following lines.

Referee one actually would welcome a revised manuscript, addressing his/her
comments and is not advising a rejection a priori. The mentioned work of
Stutman et al has an intrinsic limitation (the tilt angle) which our
approach does not have. Exactly this issue prevents the method of Stutman to
achieve sufficiently high-aspect ratio \emph{and} curved profiles at the same time, something that our method easily can. The problem mentioned on the contrast below the soldering points can be explained by beam-hardening in the absorption image. We would amend the manuscript accordingly, providing more information as requested.

Referee two is skeptical about the visibility achieved in our experiment
compared with the work from Pfeiffer's group. He/she might not have noticed
that our data have been obtained on a commercially available X-ray tube,
while the cited experiment of Pfeiffer's et al. has been carried out at a
third generation synchrotron source, where notably unsurpassed beam
conditions can be created which are far from what one can expect in real
life (i.e. with conventional X-ray tubes). And, even if one would like to
still carry out this (unfair) comparison, we should mention that our
experiment is the \emph{first} measurement of its kind with the first generation of gratings made according to our innovative design. Pfeiffer's team uses gratings obtained after almost a decade of development and, despite this and the use of a synchrotron, they are not much further than us and still carry the intrinsic limitation of a limited grating height. We are perfectly aware that the quality of our images has still to be improved, but here we are presenting the first experiments with edge-on grating illumination: we describe its great potential but also mention its (temporary) limitations. The same reviewer also complains about the limited field-of-view our method is supposed to have. This is actually wrong, since the horizontal field-of-view is just limited by the size of the wafer (as for other methods) while the vertical field-of-view is covered by a vertical scan of the sample, i.e. not limited at all, and, even more important, it becomes very interesting when CT applications are considered (all modern CT systems combine a line (or few lines) detector with a patient translation). Reviewer 2 finally admits that in comparison with a coded-aperture based experiment at 100 kVp our images (taken at 160 kVp) are better, which we of course appreciate. We believe that novelty in the approach must be the driving factor in judging the suitability of our work for this journal and not the present limitations of the technology (which can be solved!), as reviewer 2 seems to conclude.
